Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-06 SupportingInformation.Rmd
adding cache tag

```{r cause4copula_stat_ricker_clayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton

@@

```{r plot_cause4copula_stat_ricker_C, echo=F, results="hide"}

@@

```{r cause4copula_stat_ricker_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton

@@

```{r plot_cause4copula_stat_ricker_SC, echo=F, results="hide"}

@@

```{r cause4copula_stat_ricker_gumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : gumbel

@@

```{r plot_cause4copula_stat_ricker_G, echo=F, results="hide"}

@@

```{r cause4copula_stat_ricker_survivalgumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival gumbel

@@

```{r plot_cause4copula_stat_ricker_SG, echo=F, results="hide"}

@@

```{r cause4copula_stat_ricker_joe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : joe

@@

```{r plot_cause4copula_stat_ricker_J, echo=F, results="hide"}

@@

```{r cause4copula_stat_ricker_survivaljoe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival joe

@@

```{r plot_cause4copula_stat_ricker_SJ, echo=F, results="hide"}

>>>>

```{r cause4copula_stat_ricker_clayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton
tag_ricker_C<-"999C" #this is a caching tag used later to cache output from present chunk

@@

```{r plot_cause4copula_stat_ricker_C, echo=F, results="hide",cache=T, cache.extra=list(seed,tag_ricker_C,mtime("Plotter_Cause4copula.R"))}

@@

```{r cause4copula_stat_ricker_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
tag_ricker_SC<-"999SC" #this is a caching tag used later to cache output from present chunk

# This chunk stores results for ar1 model : survival clayton

@@

```{r plot_cause4copula_stat_ricker_SC, echo=F, results="hide",cache=T, cache.extra=list(seed,tag_ricker_SC,mtime("Plotter_Cause4copula.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------

@@

```{r cause4copula_stat_ricker_gumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
tag_ricker_G<-"999G" #this is a caching tag used later to cache output from present chunk

# This chunk stores results for ar1 model : gumbel

@@

```{r plot_cause4copula_stat_ricker_G, echo=F, results="hide",cache=T, cache.extra=list(seed,tag_ricker_G,mtime("Plotter_Cause4copula.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------

@@

```{r cause4copula_stat_ricker_survivalgumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
tag_ricker_SG<-"999SG" #this is a caching tag used later to cache output from present chunk

# This chunk stores results for ar1 model : survival gumbel

@@

```{r plot_cause4copula_stat_ricker_SG, echo=F, results="hide",cache=T, cache.extra=list(seed,tag_ricker_SG,mtime("Plotter_Cause4copula.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------

@@

```{r cause4copula_stat_ricker_joe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
tag_ricker_J<-"999J" #this is a caching tag used later to cache output from present chunk

# This chunk stores results for ar1 model : joe

@@

```{r plot_cause4copula_stat_ricker_J, echo=F, results="hide",cache=T, cache.extra=list(seed,tag_ricker_J,mtime("Plotter_Cause4copula.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------

@@

```{r cause4copula_stat_ricker_survivaljoe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
tag_ricker_SJ<-"999SJ" #this is a caching tag used later to cache output from present chunk

# This chunk stores results for ar1 model : survival joe

@@

```{r plot_cause4copula_stat_ricker_SJ, echo=F, results="hide",cache=T, cache.extra=list(seed,tag_ricker_SJ,mtime("Plotter_Cause4copula.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
